Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/discussions.tex
.

More generally, the continuous-time analysis should in principle be repeated for every component of  
a system. For instance, if a recurrent model is used to handle state memory or partial observability, care should be taken that the model is able to maintain moemry for a non-infinitesimal physical-time when $\deltat\to 0$ (see for instance \TODO{chronornn}).

>>>>

More generally, the continuous-time analysis should in principle be repeated for every component of  
a system. For instance, if a recurrent model is used to handle state memory or partial observability, care should be taken that the model is able to maintain memory for a non-infinitesimal physical-time when $\deltat\to 0$ (see for instance~\citealt{chronornn}).

### 2019-01-23 paper/icml_drau/experiments.tex
.

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiment set provided here is specifically aimed at showing that
the proposed method DAU can operate efficiently on a wide range of time
discretizations, without specific tuning, while standard deep Q-learning
approaches cannot. DAU is compared to DDPG in continuous action settings and to DQN in
discrete action settings.
We work off-policy; this excludes methods such as \TODO{(A3C, PPO, TRPO, ...)}.

@@

\paragraph{Qualitative experiments: Visualizing policies and values.}
To provide qualitative results, and check robustness to time
discretization both in terms of raw return results and in terms
of convergence of the approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  Its state space is of
dimension $2$. We visualize both the learnt value and policy functions by
plotting, for each point of the phase diagram $(\theta, \dot{\theta})$,
its value and policy. The results are presented in
Fig.~\ref{fig:pend} (policy function) and in Fig.\TODO{ref} in
Supplementary \TODO{ref} (value function).

>>>>

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiment set provided here is specifically aimed at showing that
the proposed method DAU can operate efficiently on a wide range of time
discretizations, without specific tuning, while standard deep Q-learning
approaches cannot. DAU is compared to DDPG in continuous action settings and to DQN in
discrete action settings.
Since our focus is the study of Q-learning based off-policy methods, we do not
compare against on-policy methods such as A3C~\cite{a3c}, PPO~\cite{ppo} or
TRPO~\cite{trpo}.

@@

\paragraph{Qualitative experiments: Visualizing policies and values.}
To provide qualitative results, and check robustness to time
discretization both in terms of raw return results and in terms
of convergence of the approximate value function and policies, we first provide results on the simple pendulum environment
from the OpenAI Gym classic control suite.  Its state space is of
dimension $2$. We visualize both the learnt value and policy functions by
plotting, for each point of the phase diagram $(\theta, \dot{\theta})$,
its value and policy. The results are presented in
Fig.~\ref{fig:pend} (value function) and in Fig.~1, 2 and 3 in
Supplementary.

### 2019-01-23 paper/icml_drau/relatedworks.tex
.

Our study focuses on off-policy algorithms. Some on-policy algorithms, such as
A3C \TODO{cite}, or PPO \TODO{cite} may be time discretization invariant in
specific setups. This would require a separate study.

>>>>

Our study focuses on off-policy algorithms. Some on-policy algorithms, such as
A3C~\cite{a3c}, or PPO~\cite{ppo} may be time discretization invariant in
specific setups. This is out of the scope of our work and would require a
separate study.
